Title here

### 2016-12-11 portfolio/text/ms.Rmd
Editing portfolio paper

```{r set-knitr-options, cache=FALSE, echo=FALSE}
library("knitr")
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, results='hide')
```
```{r get-dat}
load("../data-generated/output-values.rda")
h1 <- readRDS("../data-generated/h1_effect.rds")
spoke <- readRDS("../data-generated/spoke_fraction.rds")
g2_dens <- readRDS("../data-generated/g2_prob_dens_above_zero.rds")
n_grouped_permits <- readRDS("../data-generated/n_grouped_permits.rds")
```

@@

\bigskip
\noindent

@@

<!-- Extra: -->

<!-- - there is often limited room for intentional diversification within a permit -->
<!-- - in fact, specializing can be profitable within some fisheries -->
<!-- - Eric: analog here in farming literature is that diversification -->
<!--   for small scale farmers generally good, except when they -->
<!--   specialize on high demand/high value crops (tobacco, cocoa). -->
<!--   Seems like benefits of diversification are also smaller for -->
<!--   large-scale industrial farmers. -->

<!-- \noindent -->
<!-- Main message: -->
<!-- Diversified portfolios of fishing permits and species reduce risk for fishermen, -->
<!-- but changing species diversity can be risky, costly, and limited by regulations. -->

<!-- , which is concerning  -->
<!-- given that some fishing regulations and market forces -->
<!-- may be increasingly promoting specialization. -->
<!-- Main message in 25 words or less: -->

<!-- Take 1: -->
<!-- - There is a trend towards specializing on single salmon permits in Alaska -->
<!-- - Diversified portfolios of fishing permits and species reduce risk, -->
<!--   but changing species diversity for an individual permit holder can be risky -->
<!-- - The types of diversity needed to reduce risk are often restricted by -->
<!--   cost and regulations -->

<!-- Take 2: -->
<!-- - The effect of species diversification on revenue and risk for fishermen -->
<!-- depends on the type of diversification and the fishery. -->

<!-- Goal: Introduction, Methods, Results, Discussion, Conclusion:
<!-- 600, 900, 500, 800, 200, -->

@@

### Take homes / summary

- Suggests it's mostly an across strategy/permit effect (lowering variability),
  which isn't always a possibility because of regulations and cost
- Adjusting within current permit constraints is risky... Not clearly risk
  reducing to generalize from one year to the next
- not as simple as increase diversity (within permit) and reduce risk
- What's methodologically novel
    - Huge dataset
    - Permit level data (on individuals, not vessels)
    - Account for covariates
    - Accounting for strategies
    - Keeping annual data (not condensing to mean and cv)
    - Joint modelling of mean and variance
    - look at different mechanisms of diversification
- 2 dimensions to think about (revenue and variability); and the trade-off is fishery specific
    - effects within a permit strategy are permit specific
    - Importantly it's a tradeoff - 2 dimensions - sometimes make more money by specializing... Some highly variable single species permits make a ton of money... which preferable?

@@

- How fit in with K and H?

- EW: part of the difference is individuals vs vessels. For example, K&H
suggested that diversity declined following IFQs for halibut sablefish
vessels. The reason for the decline was that the vessels were allowed to
fish halibut for more days (because people were sharing boats). At the level
of people, we wouldn't expect the diversity of someone who only had
halibut/sablefish permit to be affected by IFQs. The person, not the vessel
holds the quota share: https://alaskafisheries.noaa.gov/fisheries/ifq
- Year to year risky... But maybe evens out/better over time
- diversity within permit - often bycatch, limited room for intentional diversification (unless you have a M or salmon permit)
- Risk results not really risk, but unpredictability given our covariates ...
don't change anything and it's most predictable how well you'll do
- What's unpredictable in our model, might be more predictable on a year to
year, species by species basis for individual permit holder
- Equilibrium, average variability vs year to year effect for one person

@@

- limitations...
- Vary by time
- Vary by mean diversity
- Spatial variation
- Nonlinear effects
- Response to specific events like EVOS and ITQs

@@

- if this is true, this is concerning because in many areas of the world and
fisheries, regulations and market forces have encouraged specialization
- Permit diversity result: a privileged position - expensive to get to into
(quote king crab license)
- Locking into permits limits ability to pick lower risk strategies and is
getting people locked into low diversity permits that may be doing well now,
but not necessarily always

@@

<!-- Ole: I'd use tau (or something) for the variances here so that people don't have to look at the subscripts to differentiate between variances at different hierarchical levels. -->

>>>>

```{r set-knitr-options, echo=FALSE}
library("knitr")
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, results="hide")
```
```{r get-dat}
load("../data-generated/output-values.rda")
h1 <- readRDS("../data-generated/h1_effect.rds")
spoke <- readRDS("../data-generated/spoke_fraction.rds")
g2_dens <- readRDS("../data-generated/g2_prob_dens_above_zero.rds")
n_grouped_permits <- readRDS("../data-generated/n_grouped_permits.rds")
```

<!-- Diversified portfolios of fishing permits and species reduce risk for fishermen, -->
<!-- but changing species diversity can be risky, costly, and limited by regulations. -->
<!-- Goal: Introduction, Methods, Results, Discussion, Conclusion:
<!-- 600, 900, 500, 800, 200, -->

@@

@@

@@

### Summary

- suggests it's mostly an across strategy/permit effect (lowering variability),
  which isn't always a possibility because of regulations and cost
- adjusting within current permit constraints is risky... Not clearly risk
  reducing to generalize from one year to the next, and accounting for effort,
  specializing can increase revenue
- not as simple as increase diversity (within permit) and reduce risk
- methodologically novel: individuals, huge dataset, account for covariates,
  accounting for strategies, keeping annual data (not condensing to mean and
  cv), joint modelling of mean and variance, evaluating within and across
  strategies (different mechanisms of diversification)
- 2 dimensions to think about (revenue and variability); and the trade-off is
  fishery specific: effects within a permit strategy are permit specific;
  sometimes make more money by specializing... some highly variable single
  species permits make a ton of money

@@

- why variability/uncertainty might increase with changes in diversity...
- and how fit in with @kasperski2013, @sethi2012b, @sethi2014
- part of the difference is individuals vs vessels. E.g. @kasperski2013
  suggested that diversity declined following IFQs for halibut sablefish
  vessels. The reason for the decline was that the vessels were allowed to fish
  halibut for more days (because people were sharing boats). At the level of
  people, we wouldn't expect the diversity of someone who only had
  halibut/sablefish permit to be affected by IFQs. The person, not the vessel
  holds the quota share: https://alaskafisheries.noaa.gov/fisheries/ifq
- year to year risky... But maybe evens out/better over time
- diversity within permit - often bycatch, limited room for intentional
  diversification (unless you have a M or salmon permit)
- risk results not really risk, but unpredictability given our covariates ...
  don't change anything and it's most predictable how well you'll do. What's
  unpredictable in our model, might be more predictable on a year to year,
  species by species basis for individual permit holder
- CV vs year-to-year effect for one person

Other:

- specializing can be profitable within some fisheries. Eric: analog here in
  farming literature is that diversification for small scale farmers generally
  good, except when they specialize on high demand/high value crops (tobacco,
  cocoa). Seems like benefits of diversification are also smaller for
  large-scale industrial farmers.

@@

- could vary by time and vary by mean diversity
- spatial/geographic variation
- nonlinear effects
- response to specific events like EVOS

@@

- concerning because in many areas of the world and fisheries, regulations and
  market forces have encouraged specialization
- permit diversity result: a privileged position --- expensive to get into
- locking into permits limits ability to pick lower risk strategies and is
  getting people locked into low diversity permits that may be doing well now,
  but not necessarily always

@@
